Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-05 Manuscript/manuscriptPSsuppl.tex
update manuscriptPSsupp.tex
Simulation details with lipid17 force field are added.

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium} \\
The data in Table \ref{mixedIONsystems} and Refs \citenum{lipid17_cacl_series,POPCpopsLIPID17withCaCl} 
\todo{B. Kav and J. Melcr, please write simulation details} \\

>>>>

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium} \\
The data in Table \ref{mixedIONsystems} and Refs \citenum{lipid17_cacl_series,POPCpopsLIPID17withCaCl}

One set of simulations of POPC:POPS (5:1) mixtures with additional calcium ions has been performed using Amber18 simulation package. Number of ions and water molecules for this set of simulations are shown in Table~\ref{mixedIONsystems}. The simulation details, minimization, heating, and equilibration runs are the same as described above for the other POPC:POPS (5:1) simulations with Amber Lipid17 forcefield. For all simulations, ff99SB~\cite{aqvist90} ion parameters and Amber lipid 17 force field were used. For each ion concentration, 100~ns equilibration runs were followed by 300~ns production runs with two independent trajectories, of which last 200~ns were used for the analysis. The trajectory files can be found in Ref~\citenum{POPCpopsLIPID17withCaCl} 
\todo{B. Kav and J. Melcr, please write simulation details} \\
